### 2017-03-29 thesis/latex/thesis.tex
Thesis: another minor commit.

@@

@@

\subsection{Parameter fitting}
There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$. Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}. Others are more difficult to find.\\

What's more, using exact literature values for each parameter does not necessarily create the simulation most similar to \textit{in vivo} dynein. Defects and simplifications in the model may cause slightly less physical values for individual parameters to lead to a more physical simulation. For this reason, fitting model parameters to experiment is necessary. This process is chronicled below. Table \ref{table:parameter-table} concisely lists literature values for various parameters.

@@

\subsubsection{Fitting rate constants}
\paragraph{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively. One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations. In contrast, the rates the model uses represent the probability of unbinding of a specific conformation. Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$. As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:

\paragraph{Literature values for experimental binding rates}
Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.

\paragraph{Fitting rate constants to processivity and step times}
Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:

\paragraph{Fitting rate constants by simulation}
\textit{Add in a plot of the binding rate fitting search}\\

To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions. The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}. Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

%% \subsubsection{Fitting spring constants}
%% \paragraph{Using $\Delta G_{bind}$ to guess $c_b$}
%% \paragraph{Using $\Theta_m$ standard deviation to guess $c_m$}
%% \paragraph{Fitting rate constants by simulation}

%% \subsubsection{Finding parameters from PyMol}

%% \subsubsection{Finding the right timestep}

\section{Chapter: Results}

\subsection{Simulation parameters}
The ideal set of parameters used to generate data were found to be:

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
    \hline
    $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
    21.0nm & 22.0nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ & 90 & 2000 & 0.5 & 2.2  & 3.1\\ \hline
  \end{tabular}
  \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
  \label{final-parameter-table}
\end{figure}

\subsection{Histograms}

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
%%     \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
%%   \end{minipage}
%%   \hspace{.1cm}
%%   \begin{minipage}[b]{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
%%     \caption{Histogram of simulated stepping times using ideal dynein parameters. Todo: superimpose Weihong's histogram of the same.}
%%   \end{minipage}
%%   \label{fig:final-histograms}
%% \end{figure}

>>>>

\usepackage{float}

@@

\subsection{Data interpretation}
Metrics for quality are required to assess how well the model fits reality. These metrics include time spent in one/bothbound states and average step size. These metrics are developed here.\\

\subsubsection{Converting experimental rates to preexponential factors $A_b$ and $A_{ub}$}
Rate constants $k_b$ and $k_{ub}$ govern the probability of transitioning from onebound to bothbound and vice-versa, respectively. One issue is that when these parameters are measured experimentally, the values represent the average rate for an ensemble of dynein in many different conformations. In contrast, the rates the model uses represent the probability of unbinding of a specific conformation. Thus, it is necessary to find a way to convert between experimental rates $k_b^{exp}$ and $k_{ub}^{exp}$ and conformation-specific rates $k_b$ and $k_{ub}$. As shown in Section \ref{sec:transitioning-states}, rates can be expressed using the Arrhenius equation:

\subsubsection{Literature values for experimental binding rates}
Sarlah \textit{et. al.} \cite{sarlahmodel} perform a similar simulation of dynein and provide the reaction rates shown in Figure \ref{fig:sarlah-rate-table}.

\subsubsection{Calculating one/bothbound times of experimental dynein}
Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:

@@

\subsection{Parameter fitting}
There are 14 free variables in the dynein model: rigid rod lengths $L_s$ and $L_t$, domain radii $R_b$, $R_m$ and $R_t$, spring constants $c_b$, $c_m$ and $c_t$, equilibrium angles $\theta_{b,eq}$, $\theta_{t,eq}$, $\Theta_{m,eq}^{Pre}$, $\Theta_{m,eq}^{Post}$, onebound binding rate $k_b$, and bothbound unbinding rate $k_{ub}$. Some of these values are found easily from literature or by looking at crystal structures of the motor protein, as shown in Table \ref{parameter-table}.\\

Others are more difficult to find. These values, including $k_b$, $k_ub$ and the three spring constants, are fit by an optimization process. First un/binding rates are fit to one/bothbound times, then spring constants are fit to average step length. This process is chronicled below.

@@

\subsubsection{Fitting rate constants}
To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions. The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}. Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

\subsubsection{Fitting spring constants}
This section will be written once it is conducted. This is contingent on getting rate fitting done, and preferably high-dt simulations stable so an optimization process can be run.\\

\section{Chapter: Results}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\

\begin{figure}[H]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
    \hline
    $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
    21.0nm & 11.15nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ &  &  &  &   & \\ \hline
  \end{tabular}
  \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
  \label{table:final-parameter-table}
\end{figure}

Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/length_histogram_sample.pdf}
    \caption{Histogram of simulated stepping lengths using ideal dynein parameters. Todo: make these figures compare better.}
  \end{minipage}
  \hspace{.1cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/time_histogram_sample.pdf}
    \caption{Histogram of simulated stepping times using ideal dynein parameters.}
  \end{minipage}\\
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Experimental dynein step size from \cite{weihongpaper}.}
  \end{minipage}
  \hspace{.1cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-velocity.pdf}
    \caption{Experimental dynein step time from \cite{weihongpaper}}
  \end{minipage}
  \label{fig:final-histograms}
\end{figure}
